The Changing Face of Pediatric Pulmonary Exacerbations in CF (NACFC 2023)

### 2023-04-14 Scott Sagel/PEx in CF/nacfc_2023.qmd
Update nacfc_2023.qmd

bugs <- c("P. aeruginosa", "P. aeruginosa mucoid", "P. aeruginosa non-mucoid", "Staph aureus", "MRSA", "S. maltophilia")

@@

>>>>

bugs <- c("Staph aureus", "MRSA", "Haemophilus influenzae", "P. aeruginosa non-mucoid", "P. aeruginosa mucoid", "Pseudomonas not aeruginosa", "Burkholderia", "burkhodescription_other", "A. xylosoxidans", "Achromobacter not xylosoxidans", "S. maltophilia", "Inquilinus limosus", "Pandoraea species", "Other bacteria", "Aspergillus species", "Candida species", "Pencillium species", "Scedosporium species", "Mycobacterium avium complex", "Other mycobacterium", "P. aeruginosa")

@@

# Write cleaned data
write.csv(df,file = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Scott Sagel/PEx in CF/Data_Clean/pex_merged.csv",row.names = F,na = "")
